Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-09 paper.tex
reformat text

	Alluxio, formerly known as Tachyon, is an in-memory file system designed to improve read and write performance without impacting fault tolerance of the system. As write performance is impeded by the need to replicate data, Tachyon leverages the concept of lineage to recompute the output if data is lost. Tachyon exhibits 110x faster write throughput than in-memory HDFS and 4.4x faster end-to-end latency. 
	\subsection{triple-H}

	%%%In other words, such frameworks would try to limit data movement, as network cables are expected to have low bandwidth and high latency. In addition, each node in a commodity cluster is expected to have access to its own local storage homogenous to that of the rest of the cluster, thus replication is necessary to ensure data availability. This is, however, not necessarily the case for computing grids. Computing grids may have access to Infinibands, which provide high bandwidth and low latency. Moreover, grids may use heterogenous storage in addition to a parallel file system such as Lustre. As a result, it may, in some cases, be faster to transfer data over the network than to access the nearest copy of the data. As well, data replication may burden a system with centralized storage as multiple copies of the data would be created, taking a significant amount of space.%%%

	%%%Big Data frameworks were not designed with high-performance computing in mind. Big Data filesystems such as were intended to run in data centers with homogenous storage (ex. HDDs, SDDs. etc,.). In such infrastructures, data movement is expensive. To counteract this, strategies were employed to avoid moving data around (data locality). In contrast, HPC clusters use heterogenous storage (ex. a combination of HDD, SSD, Ram Disk and Parallel file systems) with compute nodes connected by high-performance interconnects. HPC nodes may therefore not all be equipped with the same type of storage devices, some of which may be faster than others. Unlike data centers, HPC compute nodes do not have local storage. Moreover, the high-performance interconnects ensure low latency and high throughput of the system. In some instances, it may be even more performant to move data around rather than ensuring data locality. When a single-node HPC cluster using the Luster parallel file system was compared to a workstation with local SSD, it was found that Spark performed about 4x slower on the HPC cluster \cite{Chaimov:2016}.  As HDFS is not conscientious of the underlying infrastructure and expects a data center-type infrastructure, it cannot achieve its full performance potential. %%%

@@

	%%%Using Spark against a typical HPC parallel file system such a Luster has been found to impede scalability. This was found to be due the file system metadata latency, which limits Spark scalability to \textit{O}(10\textsuperscript{2}) cores \cite{Chaimov:2016}.

	%%%Compute Grids, interconnected networks of computing resources, are heavily used in scientific research for the processing of data. Due to their use and importance to the scientific community, it is necessary that big data frameworks used for processing neuroimaging data are compatible with them. Compute grids typically utilize heterogenous storage, such as a mixture of SSD, HDD, RAM Disk and parallel file systems (e.g. Luster). However, big data frameworks, such as Spark are designed to work efficiently with homogenous storage. Such differences result in reduced performance and inefficient storage use when big data frameworks are used on HPC clusters. This chapter will review the difference techniques applied to big data frameworks as well as HPC and grids to improve collocation of both services.%%%

	%%%\subsection{Anatomy of Grid storage}
	%%%Typical grids consist of a cluster of data nodes possibly connected to local storage (e.g. RAM Disk, HDD, SDD), but is also connected through a network to another cluster representing a parallel file system such as Lustre. RAM Disk is the fastest storage as all data is located in memory, whereas SSD provides slightly slower, persistent storage, but is a good alternative for big data. HDDs are the least performant form of local storage.%%% 
	%%%Lustre is a stateful, object-based parallel file system. It consists of three components: 1) the meta data server (MDS), 2) the Object Storage Server (OSS) and 3) the Luster Network (LNET), which enables clients to communicate with each other.%%%

>>>>

    Alluxio, formerly known as Tachyon, is an in-memory file system designed to
improve read and write performance without impacting fault tolerance of the
system. As write performance is impeded by the need to replicate data, Alluxio
leverages the concept of lineage to recompute the output if data is lost.
Tachyon exhibits 110x faster write throughput than in-memory HDFS and 4.4x
faster end-to-end latency.

    Alluxio has is made up of two layers: the lineage layer and the persistence
layer. The lineage layer is the layer that performs recomputations to obtain the
desired output. The persistance layer contains all the code used to regenerate
the data, in addition to any data that cannot be recovered through lineage
as it may be too large to fit in memory or has no lineage information stored.

    \subsection{triple-H}

    %%%In other words, such frameworks would try to limit data movement, as
    %network cables are expected to have low bandwidth and high latency. In
    %addition, each node in a commodity cluster is expected to have access to
    %its own local storage homogenous to that of the rest of the cluster, thus
    %replication is necessary to ensure data availability. This is, however, not
    %necessarily the case for computing grids. Computing grids may have access
    %to Infinibands, which provide high bandwidth and low latency. Moreover,
    %grids may use heterogenous storage in addition to a parallel file system
    %such as Lustre. As a result, it may, in some cases, be faster to transfer
    %data over the network than to access the nearest copy of the data. As well,
    %data replication may burden a system with centralized storage as multiple
    %copies of the data would be created, taking a significant amount of
    %space.%%%

    %%%Big Data frameworks were not designed with high-performance computing in
    %mind. Big Data filesystems such as were intended to run in data centers
    %with homogenous storage (ex. HDDs, SDDs. etc,.). In such infrastructures,
    %data movement is expensive. To counteract this, strategies were employed to
    %avoid moving data around (data locality). In contrast, HPC clusters use
    %heterogenous storage (ex. a combination of HDD, SSD, Ram Disk and Parallel
    %file systems) with compute nodes connected by high-performance
    %interconnects. HPC nodes may therefore not all be equipped with the same
    %type of storage devices, some of which may be faster than others. Unlike
    %data centers, HPC compute nodes do not have local storage. Moreover, the
    %high-performance interconnects ensure low latency and high throughput of
    %the system. In some instances, it may be even more performant to move data
    %around rather than ensuring data locality. When a single-node HPC cluster
    %using the Luster parallel file system was compared to a workstation with
    %local SSD, it was found that Spark performed about 4x slower on the HPC
    %cluster \cite{Chaimov:2016}.  As HDFS is not conscientious of the
    %underlying infrastructure and expects a data center-type infrastructure, it
    %cannot achieve its full performance potential. %%%

@@

    %%%Using Spark against a typical HPC parallel file system such a Luster has
    %been found to impede scalability. This was found to be due the file system
    %metadata latency, which limits Spark scalability to
    %\textit{O}(10\textsuperscript{2}) cores \cite{Chaimov:2016}.

    %%%Compute Grids, interconnected networks of computing resources, are
    %heavily used in scientific research for the processing of data. Due to
    %their use and importance to the scientific community, it is necessary that
    %big data frameworks used for processing neuroimaging data are compatible
    %with them. Compute grids typically utilize heterogenous storage, such as a
    %mixture of SSD, HDD, RAM Disk and parallel file systems (e.g. Luster).
    %However, big data frameworks, such as Spark are designed to work
    %efficiently with homogenous storage. Such differences result in reduced
    %performance and inefficient storage use when big data frameworks are used
    %on HPC clusters. This chapter will review the difference techniques applied
    %to big data frameworks as well as HPC and grids to improve collocation of
    %both services.%%%

    %%%\subsection{Anatomy of Grid storage} %%Typical grids consist of a cluster
    %of data nodes possibly connected to local storage (e.g. RAM Disk, HDD,
    %SDD), but is also connected through a network to another cluster
    %representing a parallel file system such as Lustre. RAM Disk is the fastest
    %storage as all data is located in memory, whereas SSD provides slightly
    %slower, persistent storage, but is a good alternative for big data. HDDs
    %are the least performant form of local storage.%%% %%Lustre is a stateful,
    %object-based parallel file system. It consists of three components: 1) the
    %meta data server (MDS), 2) the Object Storage Server (OSS) and 3) the
    %Luster Network (LNET), which enables clients to communicate with each
    %other.%%%
